{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
Completed to proofreading on KCF part.

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter is a well, known single target
tracking method and thetheory and its workflowhas been detailed in
other papers already
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevantto thisstudy. Its
computational efficiency arises from its use of the discrete Fourier
transform of the circulant matrix and frequency domain. The KCF
essentially solves the problem of a regression in the form of the
regularized ridge regression as:
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equaiton \ref{eq:Closedform_RidgeReg} can be computed by
taking the derivative of $E$ w.r.t $w$ to $0$. To make this,
$\mathcal{0}(n^{3})$ solution more tractable, an element-wise,
multiplication in frequency domain was proposed as a sub-linear
solution for $\hat{w}$:
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
To make the above, closed-form solution more robust to any geometric
and photometric variations, a non-linear version is also proposed
\cite{henriques2015high}.
%\begin{equation}
%\alpha = y(K+\lambda I)^{-1}
%\end{equation}
%where $K$ and $\alpha$ represent the kernel matrix and corresponding
%dual space solution. 
%\cite{henriques2015high} states that kernel
%matrices is circulant for datasets of circular cylic satisfying the
%following theorem.
%\begin{equation}
%k(x,x^{'}) = k(Mx,Mx^{'}),
%\label{eq:KernelCirculantTheorem}
%\end{equation}
%where $M$ represents the permutation matrix. Some kernels satisfying
%the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
%\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
%kernels. 
The diagonalized Fourier domain dual form solution can be
expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
%\begin{equation}
%k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
%\label{eq:GaussianCorrelationSingleChannel}
%\end{equation}
The first correlation filter based trackers used grayscale feature ($C=1$) to
learn the solution vector $w$, however, multi-channel features
such as HoG and Color were later exploited to improve tracking
accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
\begin{comment}The multi-channel feature integration into the Gaussian Kernelization
function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
in a very straight-forward way by summing the correlation result over the channels.

Training shown in eq.~\ref{eq:FourierDualDomainSolution}
gives us $\hat{a}$ learned in time step $t$. We can accumulate
$\hat{a}$ over time to integrate more temporal information. This can
be expressed as
\begin{equation}
\hat{a}_{t} = (1-\beta)\hat{a}_{t-1} + \beta\hat{a}_{t}. 
\end{equation}
\end{comment}
Finally, detection step in multi-channel KCF framework is performed as
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

>>>>

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter is a well, known single target
tracking method and thetheory and its workflowhas been detailed in
other papers already
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevantto thisstudy. Its
computational efficiency arises from its use of the discrete Fourier
transform of the circulant matrix and frequency domain. The KCF
essentially solves the problem of a regression in the form of the
regularized ridge regression as:
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equaiton \ref{eq:Closedform_RidgeReg} can be computed by
taking the derivative of $E$ w.r.t $w$ to $0$. To make this,
$\mathcal{0}(n^{3})$ solution more tractable, an element-wise,
multiplication in frequency domain was proposed as a sub-linear
solution for $\hat{w}$:
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
In fact, a non-linear version of this closed-form solution is proposed
to make it more robust to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized Fourier
domain dual form solution is expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $w$ and multi-channel features
such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. Specifically,
one can execute an object detection using this kernelized correlation
filter with multi-channel features as 
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.
